---
title: "Term Structure in High Frequency"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        number_sections: FALSE
        df_print: kable
        css: style.css
        code_folding: hide
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(
  warning=FALSE,
  message=FALSE,
  fig.width=8,
  fig.height=10
)
```


```{r script_setup}
library(data.table)
library(ggplot2)
library(magrittr)
library(extrafont)
library(scales)
library(fBasics)
library(tseries)
library(plot3D)
library(reshape2)
library(gridExtra)

source('setup.R')
```

# 01 - Summaries

## Number of Daily Observations

```{r}
termSt[, cNObsSum, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Number of Daily Observations',
      subtitle='of Interest Rate Futures Prices',
      x='date',
      y='number of observations'
    ) +
    thesisPlotTheme
```

## Closing Prices of Interest Rate Futures
```{r}
termSt[, cCloseLobs, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Closing Prices',
      subtitle='of interest rate futures',
      x='date',
      y='closing price'
    ) +
    thesisPlotTheme
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cCloseLobs[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```


## Yields of Interest Rate Futures
```{r}
termSt[, cYieldLobs, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Yields',
      subtitle='of interest rate futures',
      x='date',
      y='yield'
    ) +
    thesisPlotTheme
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cYieldLobs[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```

### Neslon-Siegel Model Fit

```{r, fig.height=6}
rowSubset <- seq.int(1L, nrow(termSt), by=25L)
plotData <- data.frame()
for(i in 1:length(rowSubset)){
  obs <- termSt[rowSubset[i], cBetaLobs, with=FALSE]
  ts <- obs[[1]]
  betas <- unlist(obs[, 2:4])
  plotData <- rbind(plotData, fitYields(betas, ts))
}
acast(plotData, date ~ maturity, value.var='yield') %>%
  persp3D(z=., y=as.numeric(colnames(.)), x=seq(from=0, to=90, along.with=rownames(.)),
          main='Fitted Yield Curves', xlab='time', ylab='maturity', zlab='yield',
          ticktype='simple', theta=35, phi=25, facets=FALSE, col='black', expand=550, d=25,
          scale=FALSE, bty='u', lwd=0.25)
```

```{r}
plotData <- data.table()

set.seed(100)
randomObs <- sample(1:nrow(termSt), size = 16)

for(o in randomObs){
  oDate <- termSt[o, timestamp]
  
  betas <- termSt[o, cBetaLobs[-1], with=FALSE]
  fittedYields <- fitYields(betas, oDate)
  
  observedYields <- data.frame(
    maturity=c(2, 5, 10, 25),
    yield=as.vector(t(termSt[o, cYieldLobs[-1], with=FALSE])),
    type='observed',
    date=oDate
  )
  
  plotData <- rbind(plotData, fittedYields, observedYields)
}

plotData %>%
  ggplot(aes(x=maturity, y=yield)) +
    geom_point(data=plotData[type=='observed', ], aes(shape=type), size=1) +
    geom_line(data=plotData[type=='fitted', ], aes(lty=type), size=0.25) +
    facet_wrap(~ date) +
    labs(
      title='Fitted vs. the Observed Yield Curve',
      subtitle='using the Dynamic Nelson Siegel Model',
      x='maturity',
      y='yield'
    ) +
    thesisPlotTheme
```

```{r}
termSt[, .(timestamp,
           TU_yield_res = TU_yield_lobs - fitYield(ns_beta0_lobs, ns_beta1_lobs, ns_beta2_lobs, 2),
           FV_yield_res = FV_yield_lobs - fitYield(ns_beta0_lobs, ns_beta1_lobs, ns_beta2_lobs, 5),
           TY_yield_res = TY_yield_lobs - fitYield(ns_beta0_lobs, ns_beta1_lobs, ns_beta2_lobs, 10),
           US_yield_res = US_yield_lobs - fitYield(ns_beta0_lobs, ns_beta1_lobs, ns_beta2_lobs, 25))] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Residuals',
      subtitle='of yield estimates of the Dynamic Nelson Siegel Model',
      x='date',
      y='residual'
    ) +
    thesisPlotTheme
```

## Realised Variances of Yields of Interest Rate Futures
```{r}
termSt[, cYieldRV, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Realised Variance',
      subtitle='of yields of interest rate futures',
      x='date',
      y='realised variance'
    ) +
    thesisPlotTheme
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cYieldRV[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```

## Beta Estimates of the Dynamic Nelson Siegel Model

```{r}
termSt[, cBetaLobs, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Coefficient Estimates',
      subtitle='of the Dynamic Nelson Siegel Model',
      x='date',
      y='coefficient estimate'
    ) +
    thesisPlotTheme
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cBetaLobs[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```

### Augmented Dickey-Fuller Test

```{r}
res <- data.table()
for(xCol in cBetaLobs[-1]){
  termSt[[xCol]] %>%
    adf.test() %>%
    unlist() %>%
    c(series=names(termSt)[xCol]) %>%
    t() %>%
    rbind(res) ->
    res
}
res[, .(series,
        adf_stat = `statistic.Dickey-Fuller`,
        lag_order = `parameter.Lag order`,
        p.value,
        alt = alternative)]
```

## First Differences of Beta Estimates of the Dynamic Nelson Siegel Model

```{r}
termSt[, cBetaDiff, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='First Differences of Coefficient Estimates',
      subtitle='of the Dynamic Nelson Siegel Model',
      x='date',
      y='first difference of coefficient estimate'
    ) +
    thesisPlotTheme
```

### Augmented Dickey-Fuller Test

```{r}
res <- data.table()
for(xCol in cBetaDiff[-1]){
  termSt[[xCol]] %>%
    adf.test() %>%
    unlist() %>%
    c(series=names(termSt)[xCol]) %>%
    t() %>%
    rbind(res) ->
    res
}
res[, .(series,
        adf_stat = `statistic.Dickey-Fuller`,
        lag_order = `parameter.Lag order`,
        p.value,
        alt = alternative)]
```

## Realised Variances of Beta Estimates of the DNSM

```{r}
termSt[, cBetaRV, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.3) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Realised Variance',
      subtitle='of coefficient estimates of the Dynamic Nelson Siegel Model',
      x='date',
      y='realised variance'
    ) +
    thesisPlotTheme
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cBetaRV[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```
