---
title: "Term Structure in High Frequency"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        number_sections: FALSE
        df_print: kable
        css: style.css
        code_folding: hide
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(
  warning=FALSE,
  message=FALSE,
  fig.width=8,
  fig.height=10
)
```


```{r script_setup}
library(data.table)
library(ggplot2)
library(magrittr)
library(extrafont)
library(scales)
library(fBasics)
library(tseries)
library(plot3D)
library(reshape2)
library(gridExtra)
library(xtable)

source('setup.R')
```

# 01 - Summaries

## Number of Daily Observations

```{r}
termSt[, cNObsSum, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Number of Intraday Observations',
      subtitle='of Interest Rate Futures Prices',
      x='date',
      y='number of observations'
    ) +
    thesisPlotTheme
ggsaveFullPage("number_of_intraday_observations.png")
```

## Closing Prices of Interest Rate Futures

```{r}
termSt[, cCloseLobs, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Closing Prices',
      subtitle='of interest rate futures',
      x='date',
      y='closing price'
    ) +
    thesisPlotTheme
ggsaveFullPage("closing_prices.png")
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cCloseLobs[-1], with=FALSE] %>%
  latexSummaryStats(filename="closing_prices.tex", caption="Summary statistics of daily closing prices", label="tab:closing_prices")
```


## Yields of Interest Rate Futures
```{r}
termSt[, cYieldLobs, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Yields',
      subtitle='of interest rate futures',
      x='date',
      y='yield'
    ) +
    thesisPlotTheme
ggsaveFullPage("yields.png")
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cYieldLobs[-1], with=FALSE] %>%
  latexSummaryStats(filename="yields.tex", caption="Summary statistics of yields", label="tab:yields", digits=6)
```

### Neslon-Siegel Model Fit

```{r, fig.height=6}
rowSubset <- seq.int(1L, nrow(termSt), by=25L)
plotData <- data.frame()
for(i in 1:length(rowSubset)){
  obs <- termSt[rowSubset[i], cBetaLobs, with=FALSE]
  ts <- obs[[1]]
  betas <- unlist(obs[, 2:4])
  plotData <- rbind(plotData, fitYields(betas, ts))
}
acast(plotData, date ~ maturity, value.var='yield') %>%
  persp3D(z=., y=as.numeric(colnames(.)), x=seq(from=0, to=90, along.with=rownames(.)),
          main='Fitted Yield Curves', xlab='time', ylab='maturity', zlab='yield',
          ticktype='simple', theta=35, phi=25, facets=FALSE, col='black', expand=550, d=25,
          scale=FALSE, bty='u', lwd=0.25)
```

#### Nelson-Siegel Cuts

```{r}
plotData <- data.table()

set.seed(12345)
randomObs <- sample(1:nrow(termSt), size = 16)

for(o in randomObs){
  oDate <- termSt[o, timestamp]
  
  betas <- termSt[o, cBetaLobs[-1], with=FALSE]
  fittedYields <- fitYields(betas, oDate)
  
  observedYields <- data.frame(
    maturity=c(2, 5, 10, 25),
    yield=as.vector(t(termSt[o, cYieldLobs[-1], with=FALSE])),
    type='observed',
    date=oDate
  )
  
  plotData <- rbind(plotData, fittedYields, observedYields)
}

plotData %>%
  ggplot(aes(x=maturity, y=yield)) +
    geom_point(data=plotData[type=='observed', ], aes(shape=type), size=1) +
    geom_line(data=plotData[type=='fitted', ], aes(lty=type), size=0.25) +
    facet_wrap(~ date) +
    labs(
      title='Fitted vs. the Observed Yield Curve',
      subtitle='using the Dynamic Nelson Siegel Model',
      x='maturity',
      y='yield'
    ) +
    thesisPlotTheme
ggsaveFullPage("n_s_cuts.png")
```

#### Mean/Median Curve

```{r}
# takes long to compute

# plotData <- data.table()
# 
# for(o in 1:nrow(termSt)){
#   oDate <- termSt[o, timestamp]
#   betas <- termSt[o, cBetaLobs[-1], with=FALSE]
#   fittedYields <- fitYields(betas, oDate)
#   plotData <- rbind(plotData, fittedYields)
# }
# 
# plotData[, .(Mean = mean(yield),
#              Median = median(yield)), by="maturity"] %>%
#   melt(id.vars=1, measure_vars=2:3) -> plotDataSummary
# 
# plotData %>%
#   ggplot(aes(x=maturity, y=yield, group=date)) +
#     geom_line(size=0.25, alpha=0.006) +
#     geom_line(data=plotDataSummary, aes(lty=variable, x=maturity, y=value, group=NULL)) +
#     labs(
#       title='Mean and Median Estimated Yield Curve',
#       subtitle='using the Dynamic Nelson Siegel Model',
#       x='maturity',
#       y='yield'
#     ) +
#     thesisPlotTheme
# ggsaveHalfPage("median_yields.png")
```

#### Residual plot

```{r}
termSt[, .(timestamp,
           `2Y resid` = `2Y Yield` - fitYield(`Beta0 (level)`, `Beta1 (slope)`, `Beta2 (curvature)`, 2),
           `5Y resid` = `5Y Yield` - fitYield(`Beta0 (level)`, `Beta1 (slope)`, `Beta2 (curvature)`, 5),
           `10Y resid` = `10Y Yield` - fitYield(`Beta0 (level)`, `Beta1 (slope)`, `Beta2 (curvature)`, 10),
           `25Y resid` = `25Y Yield` - fitYield(`Beta0 (level)`, `Beta1 (slope)`, `Beta2 (curvature)`, 25))] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Residuals',
      subtitle='of yield estimates of the Dynamic Nelson-Siegel Model',
      x='date',
      y='residual'
    ) +
    thesisPlotTheme
ggsaveFullPage("n_s_residuals.png")
```

#### Factor Loadings

```{r}
plotData <- data.table(t(sapply(seq(0.01, 30, by=0.5), FUN = factorLoadings)))
names(plotData) <- c("maturity", "Beta0 (level)", "Beta1 (slope)", "Beta2 (curvature)")
plotData %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = maturity, y = value, lty = variable)) +
    geom_line(size=0.3) +
    labs(
      title='Factor Loadings',
      subtitle='of Dynamic Nelson-Siegel Model',
      caption=paste0('Lambda = 0.6329'),
      x='maturity',
      y='factor loading'
    ) +
    thesisPlotTheme
ggsaveHalfPage("n_s_loadings.png")
```

#### ACF of yields

```{r}
res <- numeric()
for(xCol in cYieldLobs[-1]){
    acf(termSt[[xCol]], plot=FALSE)$acf[,,1] %>%
    c(res) ->
    res
}
data.table(
  series=rep(names(termSt)[cYieldLobs[-1]], each=length(res)/4),
  acf=res,
  lag=rep(seq(0, length(res)/4-1), 4)
) %>%
  ggplot(aes(x = lag, y = acf, xend = lag, yend = 0)) +
    geom_point(size=0.7) +
    geom_segment(size=0.1) +
    facet_grid(series~.) +
    labs(
      title='Autocorrelation Function',
      subtitle='of Dynamic Nelson Siegel Model factors',
      x='lag',
      y='autocorrelation'
    ) +
    thesisPlotTheme
ggsaveFullPage("acf_dnsm_coefs.png")
```


## Realised Variances of Yields of Interest Rate Futures
```{r}
termSt[, cYieldRV, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Realised Variance',
      subtitle='of yields of interest rate futures',
      x='date',
      y='realised variance'
    ) +
    thesisPlotTheme
ggsaveFullPage("yields_rv.png")
```

## Beta Estimates of the Dynamic Nelson Siegel Model

```{r}
termSt[, cBetaLobs, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Coefficient Estimates',
      subtitle='of the Dynamic Nelson Siegel Model',
      x='date',
      y='coefficient estimate'
    ) +
    thesisPlotTheme
ggsaveFullPage("dnsm_coefs.png")
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cBetaLobs[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```

### Augmented Dickey-Fuller Test Betas

```{r}
res <- data.table()
for(xCol in cBetaLobs[-1]){
  termSt[[xCol]] %>%
    adf.test() %>%
    unlist() %>%
    c(series=names(termSt)[xCol]) %>%
    t() %>%
    rbind(res) ->
    res
}
res[, .(`Series` = series,
        `ADF Stat` = round(as.numeric(`statistic.Dickey-Fuller`), 2),
        `P-Value` = round(as.numeric(p.value), 2))] %>%
  xtable(caption="Augmented Dickey-Fuller Test of Dynamic Nelson-Siegel Model factors (alternative: stationary)", label="tab:adf_n_s_factors") %>%
    print(file="tables/adf_n_s_factors.tex")
```

### Augmented Dickey-Fuller Test Yields

```{r}
res <- data.table()
for(xCol in cYieldLobs[-1]){
  termSt[[xCol]] %>%
    adf.test() %>%
    unlist() %>%
    c(series=names(termSt)[xCol]) %>%
    t() %>%
    rbind(res) ->
    res
}
res[, .(`Series` = series,
        `ADF Stat` = round(as.numeric(`statistic.Dickey-Fuller`), 2),
        `P-Value` = round(as.numeric(p.value), 2))] %>%
  xtable(caption="Augmented Dickey-Fuller Test of yields (alternative: stationary)", label="tab:adf_yields") %>%
    print(file="tables/adf_yields.tex")
```

### ACF of factors

```{r}
res <- numeric()
for(xCol in cBetaLobs[-1]){
    acf(termSt[[xCol]], plot=FALSE)$acf[,,1] %>%
    c(res) ->
    res
}
data.table(
  series=rep(names(termSt)[cBetaLobs[-1]], each=length(res)/3),
  acf=res,
  lag=rep(seq(0, length(res)/3-1), 3)
) %>%
  ggplot(aes(x = lag, y = acf, xend = lag, yend = 0)) +
    geom_point(size=0.7) +
    geom_segment(size=0.1) +
    facet_grid(series~.) +
    labs(
      title='Autocorrelation Function',
      subtitle='of Dynamic Nelson Siegel Model factors',
      x='lag',
      y='autocorrelation'
    ) +
    thesisPlotTheme
ggsaveFullPage("acf_dnsm_coefs.png")
```


## First Differences of Beta Estimates of the Dynamic Nelson Siegel Model

```{r}
termSt[, cBetaDiff, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='First Differences of Coefficient Estimates',
      subtitle='of the Dynamic Nelson Siegel Model',
      x='date',
      y='first difference of coefficient estimate'
    ) +
    thesisPlotTheme
```

### Augmented Dickey-Fuller Test

```{r}
res <- data.table()
for(xCol in cBetaDiff[-1]){
  termSt[[xCol]] %>%
    adf.test() %>%
    unlist() %>%
    c(series=names(termSt)[xCol]) %>%
    t() %>%
    rbind(res) ->
    res
}
res[, .(series,
        adf_stat = `statistic.Dickey-Fuller`,
        lag_order = `parameter.Lag order`,
        p.value,
        alt = alternative)]
```

## Realised Variances of Beta Estimates of the DNSM

```{r}
termSt[, cBetaRV, with=FALSE] %>%
  melt(id.vars=1, measure.vars = 2:ncol(.)) %>%
  ggplot(aes(x = timestamp, y = value)) +
    geom_line(size=0.1) +
    facet_grid(variable~.) +
    scale_x_date(breaks=pretty_breaks(10)) +
    labs(
      title='Realised Variance',
      subtitle='of coefficient estimates of the Dynamic Nelson Siegel Model',
      x='date',
      y='realised variance'
    ) +
    thesisPlotTheme
ggsaveFullPage("dnsm_coefs_rv.png")
```

### Summary Statistics

```{r rows.print=100, rownames.print=TRUE}
termSt[, cBetaRV[-1], with=FALSE] %>%
  basicStats() %>%
  subset(rownames(.) %in% thesisRequiredSats)
```
