---
title: "Term Structure in High Frequency"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        number_sections: FALSE
        df_print: kable
        css: style.css
        code_folding: hide
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(
  warning=FALSE,
  message=FALSE,
  fig.width=8,
  fig.height=10
)
```


```{r script_setup}
library(data.table)
library(ggplot2)
library(magrittr)
library(extrafont)
library(scales)
library(fBasics)
library(tseries)
library(plot3D)
library(reshape2)
library(gridExtra)
library(grid)
library(xtable)

source('setup.R')
```

# 03 - Cross-Spectral Analysis

## Yields of Interest Rate Futures

```{r, fig.height=4}
cSeriesComb <- t(combn(cYieldLobs[-1], m=2))
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  plotData <- getCrossSpectrumPlotData(series, title=seriesNames)
  plotCrossSpectrum(plotData)
}
```

```{r, fig.height=4}
cSeriesComb <- t(combn(cYieldLobs[-1], m=2))
res <- matrix(nrow=length(cYieldLobs[-1]), ncol=length(cYieldLobs[-1]))
colnames(res) <- names(termSt)[cYieldLobs[-1]]
rownames(res) <- names(termSt)[cYieldLobs[-1]]
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  avgCoh <- mean(getCrossSpectrumPlotData(series, title=seriesNames)$data$coh)
  res[seriesNames[1], seriesNames[2]] <- avgCoh
}
res
```

## FD of Yields of Interest Rate Futures

```{r, fig.height=4}
cSeriesComb <- t(combn(cYieldDiff[-1], m=2))
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  plotData <- getCrossSpectrumPlotData(series, title=seriesNames)
  plotCrossSpectrum(plotData)
}
```

```{r, fig.height=4}
  avgCoherencyTable(cYieldDiff[-1], filename="avg_coh_yield_diff.tex", caption="Average coherency of first-differences of yields by frequency range", label="tab:avg_coh_yield_diff")
```

```{r}
seriesX <- termSt[, cYieldDiff[-1], with=FALSE]
seriesY <- termSt[, cYieldDiff[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="...")
# ggsaveFullPage("squared_coh_yields_rv.png")
# plotMultipleCrossSpectrum(plotData, type="phase", subtitle="...")
```

## FD of Beta Coefficients

```{r, fig.height=4}
cSeriesComb <- t(combn(cBetaDiff[-1], m=2))
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  plotData <- getCrossSpectrumPlotData(series, title=seriesNames)
  plotCrossSpectrum(plotData)
}
```

```{r}
seriesX <- termSt[, cBetaDiff[-1], with=FALSE]
seriesY <- termSt[, cBetaDiff[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="between first-differenced coefficients of Dynamic Nelson-Siegel Model")
ggsaveFullPage("squared_coh_dnsm_diff.png", landscape=TRUE)
# plotMultipleCrossSpectrum(plotData, type="phase", subtitle="...")
```

## RV of Yields of Interest Rate Futures

```{r, fig.height=4}
cSeriesComb <- t(combn(cYieldRV[-1], m=2))
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  plotData <- getCrossSpectrumPlotData(series, title=seriesNames)
  plotCrossSpectrum(plotData)
}
```

```{r}
seriesX <- termSt[, cYieldRV[-1], with=FALSE]
seriesY <- termSt[, cYieldRV[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="between realised variances of yields of interest rate futures")
ggsaveFullPage("squared_coh_yields_rv.png", landscape=TRUE)
#plotMultipleCrossSpectrum(plotData, type="phase", subtitle="...")
```

## RV of Beta Estimates of the DNSM

```{r, fig.height=4}
cSeriesComb <- t(combn(cBetaRV[-1], m=2))
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  plotData <- getCrossSpectrumPlotData(series, title=seriesNames)
  plotCrossSpectrum(plotData)
}
```

```{r}
seriesX <- termSt[, cBetaRV[-1], with=FALSE]
seriesY <- termSt[, cBetaRV[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="between realised variances of yields of interest rate futures")
ggsaveFullPage("squared_coh_dnsm_coefs_rv.png", landscape=TRUE)
plotMultipleCrossSpectrum(plotData, type="phase", subtitle="...")
```

## RV of Beta Estimates and RV of a Yield of Interest Rate Future
```{r, fig.height=4}
cSeriesComb <- as.matrix(expand.grid(cYieldRV[3], cBetaRV[-1]))
for(i in 1:nrow(cSeriesComb)){
  series <- termSt[, cSeriesComb[i, ], with=FALSE]
  seriesNames <- colnames(series)
  plotData <- getCrossSpectrumPlotData(series, title=seriesNames)
  plotCrossSpectrum(plotData)
}
```

## FD of Beta Estimates and FD of a Yield of Interest Rate Future
```{r, fig.height=4}
seriesX <- termSt[, cYieldDiff[-1], with=FALSE]
seriesY <- termSt[, cBetaDiff[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="between first-differenced coefficients of DNSM\nand first-differenced yields of interest rate futures")
ggsaveFullPage("squared_coh_dnsm_diff_yields_diff.png", landscape = TRUE)
```

## FD of Beta Estimates and RV of Beta Estimates
```{r, fig.height=4}
seriesX <- termSt[, cBetaDiff[-1], with=FALSE]
seriesY <- termSt[, cBetaRV[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="...")
plotMultipleCrossSpectrum(plotData, type="phase", subtitle="...")
# ggsaveFullPage("squared_coh_dnsm_diff_yields_diff.png")
```

## FD of Yields and RV of Yilds
```{r, fig.height=4}
seriesX <- termSt[, cYieldDiff[-1], with=FALSE]
seriesY <- termSt[, cYieldRV[-1], with=FALSE]
plotData <- getMultipleCrossSpectrumPlotData(seriesX, seriesY)
plotMultipleCrossSpectrum(plotData, type="coh", subtitle="...")
plotMultipleCrossSpectrum(plotData, type="phase", subtitle="...")
# ggsaveFullPage("squared_coh_dnsm_diff_yields_diff.png")
```
